Lesson 4 - 2 variables
========================================================

```{r}

list.files()
library(ggplot2) #library of ddplot2 load

```
***

### Scatterplots and Perceived Audience Size
Notes:

```{r}
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
names(pf)
```

Also can be read by
```{r}
read.delim('pseudo_facebook.tsv') 

```


***


### Scatterplots
Notes:

```{r Scatterplots}
qplot(x =age, y = friend_count, data = pf) #scatter plot for 2 variables
```

***

#### What are some things that you notice right away?
Response: Younger users have more friends. Vertical lines that shows that the users lied from their age

***

### ggplot Syntax
Notes: the difference between ggplot and qplot is . In ggplot we need to referance geom_point (chart type)
ggplot uses "aes" wrapper

```{r Scatter Plot ing ggplot}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() +
  xlim(13,90) #we limit the age between 13 to 90

summary(pf$age)
```
***

### Overplotting
Notes: geom_jitter --> is a key to get only the integer number in to the plot

```{r Overplotting}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/2) + # we switch geom_plot with geom_jitter  & change the transperancy of dots to %50
  xlim(13,90) #we limit the age between 13 to 90

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes: we will tranform y axis to get a better view to the data

```{r Coord_trans()}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/2, position = position_jitter(h=0)) + # we have pass position_jitter to eliminate the negative number created by jitter
  xlim(13,90) + #we limit the age between 13 to 90
  coord_trans(y = 'sqrt') # we get the square root of the data to have a better view



```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/2, position = position_jitter(h=0)) + # we have pass position_jitter to eliminate the negative number created by jitter
  xlim(13,90) + #we limit the age between 13 to 90
  coord_trans(y = 'sqrt') # we get the square root of the data to have a better view

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_jitter(alpha = 1/10, position = position_jitter(h=0)) + # we have pass position_jitter to eliminate the negative number created by jitter
  coord_trans(y = 'sqrt') # we get the square root of the data to have a better view


```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}

install.packages('dplyr')
library(dplyr)

age_groups <- group_by(pf, age) #create a new variable and assing ages from pf to it

#User the new variable and create an other one to group our age data by mean and median of the sample
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count), #take the mean of friend count and set it as friend_count_mean
          friend_count_median = median(friend_count), #take the median of friend count and set it as friend_count_median
          n = n()) # n delivers the count of observations in each group

pf.fc_by_age <- arrange(pf.fc_by_age, age) #add 'age' at the end to sort the data by age 

head(pf.fc_by_age) #run the fuction for grouped data 

```

Create your plot!

```{r Conditional Means Plot}

#### Other way to do the same thing ####
pf.fc_by_age <- pf %.%  # '%.%' allows us to chain data functions to our data set
  group_by(age)%.%
  summarise(friend_count_mean = mean(friend_count), #take the mean of friend count and set it as friend_count_mean
          friend_count_median = median(friend_count), #take the median of friend count and set it as friend_count_median
          n = n()) %.%
  arrange(age)

head(pf.fc_by_age, 20) # increase the count to 20

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf.fc_by_age,pf)
 
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

